---
title: "Swain Data"
author: "Adam Bretton"
date: "2022-08-22"
output:
  pdf_document: default
  html_document: default
---

# \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Import Data

#### Clear Workspace: "rm(list = ls())"

```{r}
rm(list = ls())
```

#### Import readxl Package

```{r}
library(readxl)
```

#### Import Data \| The data was cleaned via a hybrid of JMP-R and Excel. The original data and formulas used can be found in appendix a

```{r}
TIDESDATA8_16_22 <- read_excel("~/Desktop/NCUR 2023/TIDESDATA8.16.22.xlsx", 
    sheet = "Data")
```

# \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Cleaning & Recoding Data

#### Binge Eating Screen

```{r}
## Recoding TIDESDATA8_16_22$`Binge 1=y` into TIDESDATA8_16_22$`Binge Eating Screen`
TIDESDATA8_16_22$`Binge Eating Screen` <- as.character(TIDESDATA8_16_22$`Binge 1=y`)
TIDESDATA8_16_22$`Binge Eating Screen`[TIDESDATA8_16_22$`Binge 1=y` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Binge Eating Screen`
TIDESDATA8_16_22$`Binge Eating Screen`[is.na(TIDESDATA8_16_22$`Binge Eating Screen`)] <- "Negative"
```

#### Bulimia Eating Screen

```{r}
## Recoding TIDESDATA8_16_22$`Bulimia 1=y` into TIDESDATA8_16_22$`Bulimia Eating Screen`
TIDESDATA8_16_22$`Bulimia Eating Screen` <- as.character(TIDESDATA8_16_22$`Bulimia 1=y`)
TIDESDATA8_16_22$`Bulimia Eating Screen`[TIDESDATA8_16_22$`Bulimia 1=y` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Bulimia Eating Screen`
TIDESDATA8_16_22$`Bulimia Eating Screen`[is.na(TIDESDATA8_16_22$`Bulimia Eating Screen`)] <- "Negative"
```

#### Anorexia Eating Screen

```{r}
## Recoding TIDESDATA8_16_22$`Anorexia 1=y` into TIDESDATA8_16_22$`Anorexia Eating Screen`
TIDESDATA8_16_22$`Anorexia Eating Screen` <- as.character(TIDESDATA8_16_22$`Anorexia 1=y`)
TIDESDATA8_16_22$`Anorexia Eating Screen`[TIDESDATA8_16_22$`Anorexia 1=y` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Anorexia Eating Screen`
TIDESDATA8_16_22$`Anorexia Eating Screen`[is.na(TIDESDATA8_16_22$`Anorexia Eating Screen`)] <- "Negative"
```

#### Anorexia Eating Screen

```{r}
## Recoding TIDESDATA8_16_22$`Anorexia 1=y` into TIDESDATA8_16_22$`Anorexia Eating Screen`
TIDESDATA8_16_22$`Anorexia Eating Screen` <- as.character(TIDESDATA8_16_22$`Anorexia 1=y`)
TIDESDATA8_16_22$`Anorexia Eating Screen`[TIDESDATA8_16_22$`Anorexia 1=y` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Anorexia Eating Screen`
TIDESDATA8_16_22$`Anorexia Eating Screen`[is.na(TIDESDATA8_16_22$`Anorexia Eating Screen`)] <- "Negative"
```

#### Purging Screen

```{r}
## Recoding TIDESDATA8_16_22$`Purging 1=y` into TIDESDATA8_16_22$`Purging  Screen`
TIDESDATA8_16_22$`Purging Screen` <- as.character(TIDESDATA8_16_22$`Purging 1=y`)
TIDESDATA8_16_22$`Purging Screen`[TIDESDATA8_16_22$`Purging 1=y` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Purging Screen`
TIDESDATA8_16_22$`Purging Screen`[is.na(TIDESDATA8_16_22$`Purging Screen`)] <- "Negative"
```

#### High Risk Only

```{r}
## Recoding TIDESDATA8_16_22$`Just high risk = 1` into TIDESDATA8_16_22$`High Risk Only`
TIDESDATA8_16_22$`High Risk Only` <- as.character(TIDESDATA8_16_22$`Just high risk = 1`)
TIDESDATA8_16_22$`High Risk Only`[TIDESDATA8_16_22$`Just high risk = 1` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`High Risk Only`
TIDESDATA8_16_22$`High Risk Only`[is.na(TIDESDATA8_16_22$`High Risk Only`)] <- "Negative"
```

#### Eating Disorder Positive Screen

```{r}
## Recoding TIDESDATA8_16_22$`Just ED+ = 1` into TIDESDATA8_16_22$`Eating Disorder Positive`
TIDESDATA8_16_22$`Eating Disorder Positive` <- as.character(TIDESDATA8_16_22$`Just ED+ = 1`)
TIDESDATA8_16_22$`Eating Disorder Positive`[TIDESDATA8_16_22$`Just ED+ = 1` == "1"] <- "Positive"
```

```{r}
## Recoding TIDESDATA8_16_22$`Eating Disorder Positive` into TIDESDATA8_16_22$`Eating Disorder Positive`
TIDESDATA8_16_22$`Eating Disorder Positive` <- TIDESDATA8_16_22$`Eating Disorder Positive`
TIDESDATA8_16_22$`Eating Disorder Positive`[is.na(TIDESDATA8_16_22$`Eating Disorder Positive`)] <- "Negative"
```

#### More Recoding

```{r}
## Recoding TIDESDATA8_16_22$`High Risk (=1) Vs ED Positive (=2) Vs No Known Risk (=0)` into TIDESDATA8_16_22$`Screen Results`
TIDESDATA8_16_22$`Screen Results` <- as.character(TIDESDATA8_16_22$`High Risk (=1) Vs ED Positive (=2) Vs No Known Risk (=0)`)
TIDESDATA8_16_22$`Screen Results`[TIDESDATA8_16_22$`High Risk (=1) Vs ED Positive (=2) Vs No Known Risk (=0)` == "0"] <- "No Known Risk"
```

```{r}
TIDESDATA8_16_22$`Screen Results`[TIDESDATA8_16_22$`High Risk (=1) Vs ED Positive (=2) Vs No Known Risk (=0)` == "1"] <- "High Risk"
```

```{r}
TIDESDATA8_16_22$`Screen Results`[TIDESDATA8_16_22$`High Risk (=1) Vs ED Positive (=2) Vs No Known Risk (=0)` == "2"] <- "Eating Disorder Positive"
```

### Renaming a Column

```{r}
names(TIDESDATA8_16_22)[names(TIDESDATA8_16_22) == 'SnapChat Houurs'] <- 'Snapchat Hours'
```

```{r}
names(TIDESDATA8_16_22)[names(TIDESDATA8_16_22) == 'CDAD Phy'] <- 'CDAS Physical'
```

# \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Drop Columns & New Data Set

```{r}
df <- TIDESDATA8_16_22[ -c(2:8) ]
```

```{r}
analysis1 <- read.csv(file = 'tb1.csv')
```

# \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Analysis

### View "analysis1"

```{r}
analysis1
```

```{r}
analysis1[c(5, 7:10, 12, 17:19), 1:9]
```

### Turning the above filter into its own dataframe for future data visuilization

```{r}
analysis2 <- analysis1[c(5, 7:10, 12, 17:19), 1:9]
```

# \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

# Graphs

```{r}
library(ggplot2)
```

### Average PHQ-9 Score By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `PHQ 9 score`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average PHQ-9 Score", title = "Average PHQ-9 Score By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average GAD-7 Score By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `GAD 7 score`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average GAD-7 Score", title = "Average GAD-7 Score By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average CDAS-Physical Score By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `CDAS Physical`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average CDAS-Physical Score", title = "Average CDAS-Physical Score By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average CDAS-Psych Score By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `CDAS Psych`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average CDAS-Psych Score", title = "Average CDAS-Psych Score By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average CDAS-Total Score By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `CDAS Total`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average CDAS-Total Score", title = "Average CDAS-Total Score By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average Snapchat Usage By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `Snapchat Hours`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average Snapchat Usage", title = "Average Snapchat Usage By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Average Social Media Usage By Eating Disorder Screen Classification

```{r}
ggplot(df) +
 aes(x = `Screen Results`, y = `Avg Hours`, colour = `Screen Results`) +
 geom_boxplot(fill = "#112446") +
 scale_color_hue(direction = 1) +
 labs(x = " ", y = "Average Social Media Usage", title = "Average Social Media Usage By Eating Disorder Screen Classification", 
 color = "Classification") +
 theme_linedraw()
```

### Test Graphs


```

